# Basic UI

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

## 2.2.8 Exercises {-}

1. You can fill in the parameter, `value`, inside `textInput()`: `textInput("name", value = "Your name)`


3. 
```{r}
library(shiny)

ui <- fluidPage(
    sliderInput(inputId = "user_input",
                label = "User Input", 
                value = 10,
                min = 0, max = 100,
                step = 5,
                # Added animation
                animate = animationOptions(
                    interval = 1000,
                    loop = TRUE,
                    playButton = NULL,
                    pauseButton = NULL
                )
    )
    
)

server <- function(input, output, session) {}

shinyApp(ui, server)
```


4. The documentation states, "It's also possible to group related inputs by providing a named list whose elements are (either named or unnamed) lists, vectors, or factors. In this case, the outermost names will be used as the group labels (leveraging the  `<optgroup>` HTML tag) for the elements in the respective sublist. See the example section for a small demo of this feature."


## 2.3.5 Exercises {-}

1. 

a) `renderPrint(summary(mtcars))` should be paired with `verbatimTextOutput` since it is console output.
b) `renderText("Good morning!")` should be paired with `textOutput` since it is regular text
c) `renderPrint(t.test(1:5, 2:6))` should be paired with `verbatimTextOutput` since it is console output.
d) `renderText(str(lm(mpg ~ wt, data = mtcars)))` should be paired with `verbatimTextOutput` since it is console output.

2. 
```{r}
library(shiny)

ui <- fluidPage(
    plotOutput("plot", width = "700px", height = "300px")
)

server <- function(input, output, session) {
    output$plot <- renderPlot(plot(1:5), res = 96, 
                              alt = "Scatterplot of 5 random numbers")
}

shinyApp(ui, server)
```



3. (Borrowed from https://mastering-shiny-solutions.org/basic-ui.html#exercise-3.3.5.3)
```{r}
library(shiny)

ui <- fluidPage(
    dataTableOutput("table")
)

server <- function(input, output, session) {
    output$table <- renderDataTable(mtcars, 
                                    options = list(pageLength = 5,
                                                   ordering = FALSE, 
                                                   searching = FALSE))
}

shinyApp(ui, server)
```


4.
```{r}
library(shiny)
library(reactable)

ui <- fluidPage(
  reactableOutput("table")
)

server <- function(input, output) {
  output$table <- renderReactable({
    reactable(mtcars)
  })
}

shinyApp(ui, server)

```